Gaze model analysis

### 2023-08-10 stats/gazemodel.Rmd
adjust gaze model parts

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidyboot) # for bootstrap CIs
library(coda) # HPDinterval
library(ggpubr) # stat_cor
library(ggdist) # stat_pointinterval
library(matrixStats) # logSumExp
library(ggridges) # for geom_density_ridges
library(ggthemes) # themes for plotting
library(cowplot) # ggdraw, draw_image, plot_grid

@@

```{r dev_traj_inf}
inf_map_devp <- model_kids_dev_prior %>%
  filter(scope == "global", 
         parameter == "inference", 
         type != "sigma") %>%
  group_by(type) %>%
  summarise(mode = estimate_mode(value)) %>%
  pivot_wider(names_from = "type", values_from = "mode") %>%
  expand_grid(age = seq(0, 3, 0.1)) %>%
  mutate(sd = exp(intercept + slope * age))

@@

dev_plot <- ggplot() +
  geom_point(data = id_devp, aes(x = age, y = mode), alpha = 0.75, color = "darkgrey") +
  geom_line(data = inf_samp_devp, aes(x = age + 3, y = sd, group = paste(chain,iteration)), col = "blue", alpha = .01) +
  geom_line(data = inf_map_devp, aes(x = age+3, y = sd), col = "black", linewidth = 1.25) +
  scale_x_continuous(limits = c(3, 6), breaks = seq(3, 6, 0.5)) + 
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 0.25)) +
  coord_cartesian(ylim = c(0, 3)) +
  labs(x = "Age", y = "Inference parameter")

@@

@@

```{r u_pattern}
ind_sd <- model_kids_dev_prior %>%
  filter(scope == "id", type == "sd") %>%
  group_by(id) %>%
  summarise(sdTol = estimate_mode(value)) %>%
  left_join(tango_kids %>% rename(id = subj_id,
                          eyeCenterLY = eye_center_left_y,
                          eyeCenterLX = eye_center_left_x, 
                          eyeCenterRY = eye_center_right_y,
                          eyeCenterRX = eye_center_right_x,
                          pupilLX = pupil_final_left_x,
                          pupilRX = pupil_final_right_x,
                          targetCenterX = target_center_x,
                          targetCenterY = target_center_y) %>%
              mutate(clickDist = abs(click_dist_from_target_center_x)) %>%
              select(id, age, age_group, trial_nr, eyeCenterLX, eyeCenterLY, eyeCenterRX, eyeCenterRY, pupilLX, pupilRX, targetCenterY, targetCenterX, clickDist))

@@

priorMode <- model_kids_dev_prior %>%
  filter(scope == "global", 
         parameter == "priorSd", 
         type != "sigma") %>%
  group_by(type) %>%
  summarise(mode = estimate_mode(value))

# careful, this runs a while...
gen_model_clicks <- ind_sd_long %>%
  rowwise() %>%
  mutate(modelClick = get_click_prior(
          sdTol = sdTol,
          eyeCenterLY = eyeCenterLY,
          eyeCenterLX = eyeCenterLX, 
          eyeCenterRY = eyeCenterRY,
          eyeCenterRX = eyeCenterRX,
          targetCenterX = targetCenterX,
          pupilLX = pupilLX,
          pupilRX = pupilRX,
          targetCenterY = targetCenterY,
          priorInt = priorMode %>% filter(type == "intercept") %>% pull(mode),
          priorSlope = priorMode %>% filter(type == "slope") %>% pull(mode),
          age = age
          ))

recover_plotdata <- gen_model_clicks %>%
  mutate(
    modelClickDist = abs(modelClick - targetCenterX),
    targetBin = cut(targetCenterX, 
                    breaks=seq(from = 0, to = 1920, by =192),
                    labels=as.character(1:10))
  ) %>%
  group_by(age_group, targetBin) %>%
  summarise(
    data_mean = mean(clickDist), 
    model_mean = mean(modelClickDist)
  )

saveRDS(recover_plotdata, "../saves/gazemodel_recoverU_plotdata.rds")
# recover_plotdata <- readRDS("../saves/gazemodel_recoverU_plotdata.rds")

u_plot <- recover_plotdata %>%
  pivot_longer(cols = c(data_mean, model_mean), names_to = "source", values_to = "imprecision") %>%
  mutate(
    age_group = factor(age_group, levels = c(3, 4, 5), labels = c("3-year-olds", "4-year-olds", "5-year-olds")), 
    imprecision = imprecision / 160,
  ) %>% 
  ggplot(aes(x = targetBin, y = imprecision, col = source)) +
  geom_point(alpha = 0.8) +
  facet_grid(~ age_group) +
  scale_y_continuous(limits = c(0, 5.2), breaks = seq(0, 5, 0.5)) +
  scale_color_manual(values = c("darkgrey", "darkblue"), labels = c("Data", "Model estimate")) +
  labs(x = "Target position", y = "Imprecision in target width", color = "Source") + 
  theme_few() +
  theme(
    legend.position = c(0.84 , 0.8), # c(0,0) bottom left, c(1,1) top-right
    legend.background = element_rect(color = "darkgrey", size = 0.1), 
    legend.text = element_text(size = 8),
    strip.text = element_text(face = "bold", size = 12)
  )

u_plot
saveRDS(u_plot, "../saves/gazemodel_u_plot.rds")
ggsave("../figures/gazemodel_Uplot.png", width = 8, height = 5, scale = 1, bg = "white")
ggsave("../figures/gazemodel_Uplot.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

```{r imprecision_bin_plot}
imprecision_bin_plot <- recover_plotdata %>% 
  mutate(
    model_mean = model_mean / 160, 
    data_mean = data_mean / 160,
  ) %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin)) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Model estimated imprecision", y = "Data mean imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.2), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.2), breaks = seq(0, 5, 1))

saveRDS(imprecision_bin_plot, "../saves/gazemodel_imprecision_bin_plot.rds")
ggsave("../figures/gazemodel_imprecision_bin_plot.png", width = 8, height = 5, scale = 1, bg = "white")
ggsave("../figures/gazemodel_imprecision_bin_plot.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

## Data recovery

```{r model_vs_data}
comparison_model_data_devp <- model_kids_dev_prior %>%
  filter(scope == "id", type == "sd") %>%
  group_by(id) %>%
  summarise(model_mode = estimate_mode(value)) %>%
  left_join(
    tango_kids %>% 
      group_by(subj_id, age, age_group) %>%
      summarise(data_mean = mean(click_dist_balloons)) %>%
      rename(id = subj_id)
  )

model_vs_data_plot <- ggplot(comparison_model_data_devp, aes(x = model_mode, y = data_mean)) +
  geom_point(aes(col = age)) +
  stat_cor(method = "pearson", label.x = 0.05, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_smooth(method = "lm", col = "darkgrey", alpha = 0.25) +
  scale_color_viridis_c(direction = -1, alpha = 0.9, limits = c(3, 6), breaks = seq(3, 6, 0.5)) +
  labs(x = "Model estimated mode", y = "Data imprecision mean", color = "Age") + 
  scale_x_continuous(limits = c(0, 2.1), breaks = seq(0, 2, 0.5)) + 
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1))

model_vs_data_plot
saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")
ggsave("../figures/gazemodel_model_vs_data.png", width = 8, height = 5, scale = 1, bg = "white")
ggsave("../figures/gazemodel_model_vs_data.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

@@

```{r arrange_plot}
setup_png <- ggdraw() + draw_image("../figures/gazemodel_setup.png")
ulogic_png <- ggdraw() + draw_image("../figures/gazemodel_Ulogic.png")

@@

  ulogic_png, 
  u_plot, 
  NULL, 
  imprecision_bin_plot,

  ncol = 4, 
  nrow = 2, 
  widths = c(9, 12, 1, 11), 
  labels = c("A", "B", "", "C", "D", "E", "", "F")
)

@@

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidyboot) # for bootstrap CIs
library(coda) # HPDinterval
library(ggpubr) # stat_cor
library(ggdist) # stat_pointinterval
library(matrixStats) # logSumExp
library(ggridges) # for geom_density_ridges
library(ggthemes) # themes for plotting
library(cowplot) # ggdraw, draw_image, plot_grid
library(psych) #corr.test

@@

```{r plot2B}
# (plot 2A is model logic, png)
# developmental trajectory model inference parameter
inf_map_devp <- model_kids_dev_prior %>%
  filter(scope == "global", 
         parameter == "inference", 
         type != "sigma") %>%
  group_by(type) %>%
  summarise(mode = estimate_mode(value)) %>%
  pivot_wider(names_from = "type", values_from = "mode") %>%
  expand_grid(age = seq(0, 3, 0.1)) %>%
  mutate(sd = exp(intercept + slope * age))

@@

dev_plot <- ggplot() +
  geom_point(data = id_devp, aes(x = age, y = mode), alpha = 0.75, color = "darkgrey") +
  geom_line(data = inf_samp_devp, aes(x = age + 3, y = sd, group = paste(chain,iteration)), col = "blue", alpha = .01) +
  geom_line(data = inf_map_devp, aes(x = age+3, y = sd), col = "black", linewidth = 1.25) +
  scale_x_continuous(limits = c(3, 6), breaks = seq(3, 6, 0.5)) + 
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 0.25)) +
  coord_cartesian(ylim = c(0, 3)) +
  labs(x = "Age", y = "Model parameter")

@@

## Correlation model vs data individual level / age

```{r plot2C}
comparison_model_data_devp <- model_kids_dev_prior %>%
  filter(scope == "id", type == "sd") %>%
  group_by(id) %>%
  summarise(model_mode = estimate_mode(value)) %>%
  left_join(
    tango_kids %>% 
      group_by(subj_id, age, age_group) %>%
      summarise(data_mean = mean(click_dist_balloons)) %>%
      rename(id = subj_id)
  )

model_vs_data_plot <- ggplot(comparison_model_data_devp, aes(x = model_mode, y = data_mean)) +
  geom_point(aes(col = age)) +
  stat_cor(method = "pearson", label.x = 0.05, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_smooth(method = "lm", col = "darkgrey", alpha = 0.25) +
  scale_color_viridis_c(direction = -1, alpha = 0.9, limits = c(3, 6), breaks = seq(3, 6, 0.5)) +
  labs(x = "Model parameter", y = "Data imprecision", color = "Age") + 
  scale_x_continuous(limits = c(0, 2.1), breaks = seq(0, 2, 0.5)) + 
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1))

model_vs_data_plot
saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")
# ggsave("../figures/gazemodel_model_vs_data.png", width = 8, height = 5, scale = 1, bg = "white")
# ggsave("../figures/gazemodel_model_vs_data.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

@@

```{r plot2E}
# (plot 2D is model geometry logic, png)
# u pattern recovery
ind_sd <- model_kids_dev_prior %>%
  filter(scope == "id", type == "sd") %>%
  group_by(id) %>%
  summarise(sdTol = estimate_mode(value)) %>%
  left_join(tango_kids %>% rename(id = subj_id,
                          eyeCenterLY = eye_center_left_y,
                          eyeCenterLX = eye_center_left_x,
                          eyeCenterRY = eye_center_right_y,
                          eyeCenterRX = eye_center_right_x,
                          pupilLX = pupil_final_left_x,
                          pupilRX = pupil_final_right_x,
                          targetCenterX = target_center_x,
                          targetCenterY = target_center_y) %>%
              mutate(clickDist = abs(click_dist_from_target_center_x)) %>%
              select(id, age, age_group, trial_nr, eyeCenterLX, eyeCenterLY, eyeCenterRX, eyeCenterRY, pupilLX, pupilRX, targetCenterY, targetCenterX, clickDist))

@@

# saveRDS(ind_sd_long, file = "../saves/gazemodel_ind_sd_long.rds")

# priorMode <- model_kids_dev_prior %>%
#   filter(scope == "global",
#          parameter == "priorSd",
#          type != "sigma") %>%
#   group_by(type) %>%
#   summarise(mode = estimate_mode(value))
#

# # careful, this runs a while... (ca. 30-45 min for me)

# gen_model_clicks <- ind_sd_long %>%
#   rowwise() %>%
#   mutate(modelClick = get_click_prior(
#           sdTol = sdTol,
#           eyeCenterLY = eyeCenterLY,
#           eyeCenterLX = eyeCenterLX, 
#           eyeCenterRY = eyeCenterRY,
#           eyeCenterRX = eyeCenterRX,
#           targetCenterX = targetCenterX,
#           pupilLX = pupilLX,
#           pupilRX = pupilRX,
#           targetCenterY = targetCenterY,
#           priorInt = priorMode %>% filter(type == "intercept") %>% pull(mode),
#           priorSlope = priorMode %>% filter(type == "slope") %>% pull(mode),
#           age = age
#           ))
# 
# modelpred_gaze <- gen_model_clicks %>%
#   mutate(
#     modelClickDist = abs(modelClick - targetCenterX),
#     targetBin = cut(targetCenterX, 
#                     breaks = seq(from = 0, to = 1920, by = 192),
#                     labels = as.character(1:10))
#   ) %>%
#   group_by(age_group, targetBin) %>%
#   summarise(
#     data_mean = mean(clickDist) / 160, 
#     model_mean = mean(modelClickDist) / 160,
#   )

# saveRDS(modelpred_gaze, "../saves/gazemodel_modelpred_gaze.rds")
modelpred_gaze <- readRDS("../saves/gazemodel_modelpred_gaze.rds")

u_plot <- modelpred_gaze %>%
  pivot_longer(cols = c(data_mean, model_mean), names_to = "source", values_to = "imprecision") %>%
  mutate(
    age_group = factor(age_group, levels = c(3, 4, 5), labels = c("3-year-olds", "4-year-olds", "5-year-olds")), 
  ) %>% 
  ggplot(aes(x = targetBin, y = imprecision, col = source)) +
  geom_point(alpha = 0.8) +
  facet_grid(~ age_group) +
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5.5, 0.5)) +
  scale_color_manual(values = c("darkgrey", "darkblue"), labels = c("Data", "Model prediction")) +
  labs(x = "Target bin", y = "Imprecision", color = "Source") + 
  theme_few() +
  theme(
    legend.position = c(0.84 , 0.8), # c(0,0) bottom left, c(1,1) top-right
    strip.text = element_text(face = "bold", size = 12), 
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6), 
    legend.box.background = element_rect(), 
    legend.key.height = unit(0, "cm"),
    legend.key.width = unit(-1.5, "cm"),
    plot.margin = margin(0.2, 0, 0.1, 0.2, "cm") # t r b l
  )

u_plot
saveRDS(u_plot, "../saves/gazemodel_u_plot.rds")
# ggsave("../figures/gazemodel_Uplot.png", width = 8, height = 5, scale = 1, bg = "white")
# ggsave("../figures/gazemodel_Uplot.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

```{r modelpred_gaze_plot}
# correlation model predicted imprecision vs data imprecision across target positions
modelpred_gaze_plot <- modelpred_gaze %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin)) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Gaze model predicted imprecision", y = "Data imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

modelpred_gaze_plot
saveRDS(modelpred_gaze_plot, "../saves/gazemodel_modelpred_gaze_plot.rds")
# ggsave("../figures/gazemodel_modelpred_gaze_plot.png", width = 8, height = 5, scale = 1, bg = "white")
# ggsave("../figures/gazemodel_modelpred_gaze_plot.pdf", width = 8, height = 5, scale = 1, bg = "white")
```
# Alternative models click generation

## Center bias model

```{r get_click_center}
get_click_center <- function(){

  xDist = dnorm(seq(1:1920), mean = 960, sd = 160)

```{r center_model}
gen_model_clicks_center <- ind_sd_long %>%
  rowwise()%>%
  mutate(modelClick = get_click_center())

modelpred_center <- gen_model_clicks_center %>%
  mutate(
    modelClickDist = abs(modelClick - targetCenterX),
    targetBin = cut(targetCenterX, 
                    breaks = seq(from = 0, to = 1920, by = 192),
                    labels = as.character(1:10))) %>%
  group_by(age_group, targetBin) %>%
  summarise(
    data_mean = mean(clickDist) / 160, 
    model_mean = mean(modelClickDist) / 160, 
  )

saveRDS(modelpred_center, file = "../saves/gazemodel_modelpred_center.rds")

# facetted U plot
modelpred_center %>%
  pivot_longer(cols = c(data_mean, model_mean), names_to = "source", values_to = "imprecision") %>%
  mutate(
    age_group = factor(age_group, levels = c(3, 4, 5), labels = c("3-year-olds", "4-year-olds", "5-year-olds")), 
  ) %>% 
  ggplot(aes(x = targetBin, y = imprecision, col = source)) +
  geom_point(alpha = 0.8) +
  facet_grid(~ age_group) +
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5.5, 0.5)) +
  scale_color_manual(values = c("darkgrey", "darkblue"), labels = c("Data", "Model prediction")) +
  labs(x = "Target bin", y = "Imprecision", color = "Source") + 
  theme_few() +
  theme(
    legend.position = c(0.84 , 0.8), # c(0,0) bottom left, c(1,1) top-right
    legend.background = element_rect(color = "darkgrey", size = 0.1), 
    legend.text = element_text(size = 8),
    strip.text = element_text(face = "bold", size = 12)
  )

# corr plot
modelpred_center_plot <- modelpred_center %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin), size = 0.8) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Model predicted imprecision", y = "Data imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

modelpred_center_plot
saveRDS(modelpred_center_plot, "../saves/gazemodel_modelpred_center_plot.rds")
# ggsave("../figures/gazemodel_modelpred_center_plot.png", width = 10, height = 5, scale = 1.4, bg = "white")
# ggsave("../figures/gazemodel_modelpred_center_plot.pdf", width = 10, height = 5, scale = 1.4, bg = "white")
```

## Random clicks model

```{r get_click_random}
get_click_random <- function(){

  xDist = dunif(seq(1:1920), min = 1, max = 1920)

```{r random_model}
gen_model_clicks_random <- ind_sd_long %>%
  rowwise() %>%
  mutate(modelClick = get_click_random())

modelpred_random <- gen_model_clicks_random %>%
  mutate(
    modelClickDist = abs(modelClick - targetCenterX),
    targetBin = cut(targetCenterX, 
                    breaks = seq(from = 0, to = 1920, by = 192),
                    labels=as.character(1:10))
  ) %>%
  group_by(age_group, targetBin) %>%
  summarise(
    data_mean = mean(clickDist) / 160, 
    model_mean = mean(modelClickDist) / 160
  )

saveRDS(modelpred_random, file = "../saves/gazemodel_modelpred_random.rds")

# facetted U plot
modelpred_random %>%
  pivot_longer(cols = c(data_mean, model_mean), names_to = "source", values_to = "imprecision") %>%
  mutate(
    age_group = factor(age_group, levels = c(3, 4, 5), labels = c("3-year-olds", "4-year-olds", "5-year-olds")), 
  ) %>% 
  ggplot(aes(x = targetBin, y = imprecision, col = source)) +
  geom_point(alpha = 0.8) +
  facet_grid(~ age_group) +
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5.5, 0.5)) +
  scale_color_manual(values = c("darkgrey", "darkblue"), labels = c("Data", "Model prediction")) +
  labs(x = "Target bin", y = "Imprecision", color = "Source") + 
  theme_few() +
  theme(
    legend.position = c(0.84 , 0.8), # c(0,0) bottom left, c(1,1) top-right
    legend.background = element_rect(color = "darkgrey", size = 0.1), 
    legend.text = element_text(size = 8),
    strip.text = element_text(face = "bold", size = 12)
  )

# corr plot
modelpred_random_plot <- modelpred_random %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin), size = 0.8) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Model predicted imprecision", y = "Data imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

modelpred_random_plot
saveRDS(modelpred_random_plot, "../saves/gazemodel_modelpred_random_plot.rds")
# ggsave("../figures/gazemodel_modelpred_random_plot.png", width = 10, height = 5, scale = 1.4, bg = "white")
# ggsave("../figures/gazemodel_modelpred_random_plot.pdf", width = 10, height = 5, scale = 1.4, bg = "white")
```

## Combine plots of predictions from 3 models

```{r plot2F}
modelpred_gaze_plot <- readRDS("../saves/gazemodel_modelpred_gaze_plot.rds")
modelpred_center_plot <- readRDS("../saves/gazemodel_modelpred_center_plot.rds")
modelpred_random_plot <- readRDS("../saves/gazemodel_modelpred_random_plot.rds")

corr_model_pred_plot <- ggarrange(

  modelpred_gaze_plot + 
    theme(legend.position = c(0.85, 0.2), 
          legend.title = element_text(size = 6),
          legend.text = element_text(size = 6), 
          legend.box.background = element_rect(), 
          legend.key.height = unit(0, "cm"),
          legend.key.width = unit(-1.5, "cm"),
          plot.margin = margin(0.2, 0, 0.1, 0.2, "cm") # t r b l
         ),

  ggarrange(
    modelpred_center_plot + 
      labs(x = "Center bias model", y = "") +
      theme(legend.position = "none", 
            axis.text = element_text(size = 6), 
            axis.title = element_text(size = 8), 
            plot.subtitle = element_text(size = 8), 
            plot.margin = margin(0.2, 0.2, 0.2, 0, "cm")),

    modelpred_random_plot + 
      labs(x = "Random guessing model", y = "") +
      theme(legend.position = "none", 
            axis.text = element_text(size = 6), 
            axis.title = element_text(size = 8), 
            plot.subtitle = element_text(size = 8), 
            plot.margin = margin(0.2, 0.2, 0.2, 0, "cm")), 
    nrow = 2
  ),

  ncol = 2, 
  widths = c(1.5, 1), 
  align = "v"
  )

corr_model_pred_plot
saveRDS(corr_model_pred_plot, file = "../saves/gazemodel_corr_model_pred_plot.rds")
```

@@

```{r arrange_plot}
setup_png <- ggdraw() + draw_image("../figures/gazemodel_logic_alpha.png", scale = 0.82)
ulogic_png <- ggdraw() + draw_image("../figures/gazemodel_geometry_lines.png", scale = 0.95)

dev_plot <- readRDS(file = "../saves/gazemodel_dev_plot.rds")
model_vs_data_plot <- readRDS(file = "../saves/gazemodel_model_vs_data.rds")
u_plot <- readRDS("../saves/gazemodel_u_plot.rds")
corr_model_pred_plot <- readRDS("../saves/gazemodel_corr_model_pred_plot.rds")

@@

  ulogic_png, 
  u_plot, 
  NULL, 
  corr_model_pred_plot,

  ncol = 4, 
  nrow = 2, 
  widths = c(9, 11, 1, 11), 
  labels = c("A", "B", "", "C", "D", "E", "", "F")
)

@@

```{r results_table}
# create tibble for reading out stats results in rmd manuscript
corr_gazemodel_param <- comparison_model_data_devp %>% select(model_mode, data_mean) %>% corr.test(method = "pearson")

corr_gazemodel_pred <- modelpred_gaze %>% ungroup() %>% select(model_mean, data_mean) %>% corr.test(method = "pearson")
corr_centermodel_pred <- modelpred_center %>% ungroup() %>% select(model_mean, data_mean) %>% corr.test(method = "pearson")
corr_randommodel_pred <- modelpred_random %>% ungroup() %>% select(model_mean, data_mean) %>% corr.test(method = "pearson")

corrs <- rbind(corr_gazemodel_param$ci, corr_gazemodel_pred$ci, corr_centermodel_pred$ci, corr_randommodel_pred$ci) %>% 
  rownames_to_column(var = "corr") %>% 
  mutate(
    corr = recode(
            corr,
            `mdl_m-dt_mn` = "gazemodel_param", 
            `mdl_m-dt_mn1` = "gazemodel_pred", 
            `mdl_m-dt_mn2` = "centermodel_pred", 
            `mdl_m-dt_mn3` = "randommodel_pred", 
           )
  ) %>% 
  mutate(across(where(is.numeric), round, 2))

corrs
saveRDS(corrs, file = "../saves/gazemodel_correlations.rds")
```

# Model comparison BayesFactor
## TODO GET DATA FROM SERVER
```{r read_data_mcomparison}
# devp_model_comp <- rbindlist(
#   list(
#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain7.csv")%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike)),
#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain8.csv")%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike)),
#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain9.csv")%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike)),
#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain10.csv")%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike)),
#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain11.csv")%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike)),
#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain12.csv")%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))
#     ), use.names=TRUE)
```

```{r modelcomparison}
devp_model_comp %>%
  group_by(model,chain) %>%
  summarise(margllh = logSumExp(like)) %>%
  pivot_wider(names_from = model, values_from = margllh)

devp_model_comp %>%
  group_by(model) %>%
  summarise(margllh = logSumExp(like)) %>%
  pivot_wider(names_from = model, values_from = margllh) %>%
  summarise(bf_inf_center = inf - center, 
            bf_inf_guess = inf - guess)

devp_model_comp%>%
  ggplot(aes(x = like))+
  geom_histogram(alpha = .5, aes(fill = model), col = "black")+
  scale_fill_colorblind()+
  xlim(-8000, -5000)+
  theme_bw()
```

# Headlight distribution for plots

```{r get_dist}
# get_dist <- function(sdTol, eyeCenterLY, eyeCenterLX, eyeCenterRY, eyeCenterRX, targetCenterY, targetCenterX, pupilLX, pupilRX){
# 
#   if(eyeCenterLX > pupilLX) {
#     tAlphaL = atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
#   } else {
#     tAlphaL = -atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
#   }
#   
#   #noisyAlphaL = rnorm(1,tAlphaL, sdPer)
#   
#   if(eyeCenterRX > pupilRX) {
#     tAlphaR = atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
#   } else {
#     tAlphaR = -atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
#   }
#   
#   #noisyAlphaR = rnorm(1,tAlphaR, sdPer)
# 
#   bRDist = c()
#   
#   bLDist = c()
#   
#   for (x in 1:1920){
#     
#   if(eyeCenterLX > x) {
#     betaL = atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
#   } else {
#     betaL = -atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
#   }
#     betaLDist = dnorm(betaL,tAlphaL,sdTol, log = T)
#     
#   if(eyeCenterRX > x) {
#     betaR = atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
#   } else {
#     betaR = -atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
#   }
#     betaRDist = dnorm(betaR,tAlphaR,sdTol, log = T)
#     
#     #betaDist = betaLDist + betaRDist
#     
#     #bDist[x] <- exp(betaDist)
#     bRDist[x] <- betaRDist
#     
#     bLDist[x] <- betaLDist
#     
#   }
#   
#   xRDist = exp(bRDist-logSumExp(bRDist))
#   
#   xLDist = exp(bLDist-logSumExp(bLDist))
#   
#   xDist = xRDist * xLDist
#   
#   dist = xDist / sum(xDist)
#   
#   # click = sample(1:1920, prob = xDist, size = 1)-1
#   
#   return(dist)
# }
```

```{r headlight_dist}
# headlight_df <- data.frame(
#   coord = 1:1920,
#   sdTol = "0.175"
# )
# 
# for (i in c(960,1736)){
#   
#   probdist <-  get_dist(
#     sdTol = 0.175,
#     targetCenterX = i,
#     eyeCenterLY = 937.8,
#     eyeCenterLX = 872.12,
#     eyeCenterRY = 937.8,
#     eyeCenterRX = 1045.89,
#     targetCenterY = 127.5,
#     pupilLX = i-1,
#     pupilRX = i-1)
#   
#     colname = as.character(i)
#     
#     headlight_df[, colname] <- probdist
#   
#   }
# 
# headlight_df %>%
#   pivot_longer(names_to = "target_coordinate", values_to = "probability", cols = c(-coord, -sdTol)) %>%
#   filter(target_coordinate == "960") %>%
#   ggplot(aes(x = coord, y = probability, group = interaction(target_coordinate,sdTol))) +
#   geom_density(stat = "identity", color = "blue", fill = "blue", alpha = .5) +
#   ylim(0, 0.006) +
#   scale_x_continuous(limits = c(0, 1920), breaks = seq(0, 1920, 480)) +
#   guides(fill = F) + 
#   # geom_vline(aes(xintercept = as.numeric(target_coordinate)), lty = 2, alpha = .25) +
#   # labs(x = "Coordinate", y = "Probability") +
#   # scale_fill_colorblind(name = "Inference SD") +
#   theme_few() + 
#   theme(
#     panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
#     panel.grid.minor = element_blank(), 
#     panel.grid.major = element_blank(),
#     plot.background = element_rect(fill = "transparent",colour = NA)
# )
# 
# ggsave("../figures/gazemodel_headlight_dist_side.png", width = 15, height = 4, bg = "transparent")
# 
# ##  Standard normal dist
# dnorm_one_sd <- function(x){
#   norm_one_sd <- dnorm(x)
#   # Have NA values outside interval x in [-1, 1]:
#   norm_one_sd[x <= -1 | x >= 1] <- NA
#   return(norm_one_sd)
# }
# 
# ggplot(data.frame(x = c(-4, 4)), aes(x = x)) +
#   stat_function(fun = dnorm, color = "darkgrey", linewidth = 2) + 
#   stat_function(fun = dnorm_one_sd, geom = "area", fill = "blue", alpha = 0.5) +
#   # geom_vline(aes(xintercept = 0), lty = 2, color = "blue") +
#   theme_void()
# 
# ggsave("../figures/gazemodel_normal_dist.png", width = 10, height = 4)
```
